Presentation Title

### 2017-08-07 thesis/chapters/ch1-intro.tex
Change paper template; fix thesis template

In this work, we take the advice of Croman et el.~\cite{croman2016scaling} and Vukoli\'{c}~\cite{vukolic2015quest} and rethink the blockchain architecture.
Our primary insight came from observing the differences between how value transfer work in the real world and how they work in early blockchain systems.
Take a restaurant owner, for example,
most of the time the customer is honest and pays the bill.
There is no need for the customer or the owner to report the transaction to any central authority 
because both parties are happy with the transaction.
On the other hand, if the customer leaves without paying the bill,
then the owner would report the incident to some central authority, e.g. the police.
On the contrary, in blockchain systems, every transaction is effectively sent to the miners,
which can be seen as a collective authority.
This consequently leads to limited scalability because every transaction must be validated by the authority even when most of the transactions are legitimate.

@@

We describe and analyse our idea in the remainder of this work.
We begin with the problem description in~\Cref{ch:problem} which describes the state-of-the-art work on making blockchain systems scalable and our research question.
In~\Cref{ch:model} we give a formal description of our system model and architecture.
Next, we analyse the correctness and performance of our design in~\Cref{ch:analysis}, this is where we present our key theorems.
Implementation and experimental results are discussed in~\Cref{ch:implementation}.
Finally, we conclude in \ref{ch:conclusion} and discuss future work.

>>>>

\section{Contributions}
In this work, we take the advice of Croman et el.~\cite{croman2016scaling} and Vukoli\'{c}~\cite{vukolic2015quest} and rethink the blockchain architecture.
Our primary insight came from observing the differences between how value transfer work in the real world and how they work in early blockchain systems.
Take a restaurant owner, for example,
most of the time the customer is honest and pays the bill.
There is no need for the customer or the owner to report the transaction to any central authority 
because both parties are happy with the transaction.
On the other hand, if the customer leaves without paying the bill,
then the owner would report the incident to some central authority, e.g. the police.
On the contrary, in blockchain systems, every transaction is effectively sent to the miners,
which can be seen as a collective authority.
This consequently leads to limited scalability because every transaction must be validated by the authority even when most of the transactions are legitimate.

@@

\section{Document structure}
We describe and analyse our idea in the remainder of this work.
We begin with the problem description in~\Cref{ch:problem} which describes the state-of-the-art work on making blockchain systems scalable and our research question.
In~\Cref{ch:model} we give a formal description of our system model and architecture.
Next, we analyse the correctness and performance of our design in~\Cref{ch:analysis}, this is where we present our key theorems.
Implementation and experimental results are discussed in~\Cref{ch:implementation}.
Finally, we conclude in \ref{ch:conclusion} and discuss future work.

### 2017-08-07 thesis/chapters/ch3-model.tex
Change paper template; fix thesis template

The TX block is a six-tuple, i.e $t_{u, i} = \langle \textsf{H}(b_{u, i - 1}), seq_u, txid, pk_v, m, sig_u \rangle$.
We describe each item in turn.
\begin{enumerate}
\item $\textsf{H}(b_{u, i - 1})$ is the hash pointer to the previous block.
\item $seq_u$ is the sequence number which should equal $i$.
\item $txid$ is the transaction identifier, it should be generated using a cryptographically secure pseudo-random number generator by the initiator of the transaction.
\item $pk_v$ is the public key of the counterparty $v$.
\item $m$ is the transaction message.
\item $sig_u$ is the signature created using $sk_u$ on the concatenation of the binary representation of the five items above.
\end{enumerate}
The fact that we have no constraint on the content of $m$ is in alignment with our design goal---application neutrality.

@@

The CP block is a five-tuple, 
i.e. $c_{u, i} = \langle \textsf{H}(b_{u, i-1}), seq_u, \textsf{H}(\C_r), r, sig_u \rangle$,
where $\C_r$ is the consensus result (which we describe in \Cref{sec:consensus-result}) in round $r$, the other items are the same as the TX block definition.
% Note that unlike in our prior work~\cite{implicitconsensus}, CP blocks and TX blocks do not have independent sequence numbers.

The genesis block in the chain must be a CP block in the form of
$c_{u, 0} = \langle \textsf{H}(\bot), 0,  \textsf{H}(\bot), 0, sig_u \rangle$
where $\textsf{H}(\bot)$ can be interpreted as applying the hash function on an empty string.
The genesis block is unique because every node has a unique public and private key pair.
\end{definition}

>>>>

The TX block is a six-tuple, i.e
$$t_{u, i} = \langle \textsf{H}(b_{u, i - 1}), seq_u, txid, pk_v, m, sig_u \rangle.$$
We describe each item in turn.
\begin{enumerate}
\item $\textsf{H}(b_{u, i - 1})$ is the hash pointer to the previous block.
\item $seq_u$ is the sequence number which should equal $i$.
\item $txid$ is the transaction identifier, it should be generated using a cryptographically secure pseudo-random number generator by the initiator of the transaction.
\item $pk_v$ is the public key of the counterparty $v$.
\item $m$ is the transaction message.
\item $sig_u$ is the signature created using $sk_u$ on the concatenation of the binary representation of the five items above.
\end{enumerate}
The fact that we have no constraint on the content of $m$ is in alignment with our design goal---application neutrality.

@@

The CP block is a five-tuple, i.e. 
$$c_{u, i} = \langle \textsf{H}(b_{u, i-1}), seq_u, \textsf{H}(\C_r), r, sig_u \rangle,$$
where $\C_r$ is the consensus result (which we describe in \Cref{sec:consensus-result}) in round $r$,
the other items are the same as the TX block definition.
% Note that unlike in our prior work~\cite{implicitconsensus}, CP blocks and TX blocks do not have independent sequence numbers.

The genesis block in the chain must be a CP block in the form of
$$c_{u, 0} = \langle \textsf{H}(\bot), 0,  \textsf{H}(\bot), 0, sig_u \rangle,$$
where $\textsf{H}(\bot)$ can be interpreted as applying the hash function on an empty string.
The genesis block is unique because every node has a unique public and private key pair.
\end{definition}

### 2017-08-07 thesis/chapters/ch5-implementation.tex
Fixes
Change paper template; fix thesis template

The structure of the implementation is primarily made up of three modules---\texttt{acs}, \texttt{trustchain} and \texttt{node}.
\texttt{acs}, as its name suggests, implements ACS.
ACS uses erasure code in one of its sub-protocols (reliable broadcast).
Thus we use the liberasurecode\footnote{\url{https://github.com/openstack/liberasurecode}} library for its Reed-Solomon error correcting code functionality.
An implementation detail is that liberasurecode cannot create more than 32 code blocks\footnote{
  The 32 code blocks limitation is hardcoded in the source file, see
  \url{https://github.com/openstack/liberasurecode/blob/0794b31c623e4cede76d66be730719d24debcca9/include/erasurecode/erasurecode.h\#L35}
}, we discuss the effect of this in~\Cref{sec:experimental-setup}.
The \texttt{acs} module provides a small interface to the caller to start and stop the consensus process and also retrieve results.
The \texttt{trustchain} module implements the Extended TrustChain data structure.
It also provides the essential algorithm necessary to interact with Extended TrustChain such as 
$\textsf{new\_tx}(\cdot)$, $\textsf{new\_cp}(\cdot)$ and $\textsf{agreed\_fragment}(\cdot)$.
Finally, the \texttt{node} module ties everything together.
It implements the consensus protocol, the transaction protocol and the validation protocol.

@@

The difference in magnitude between \Cref{fig:global-throughput-fixed} and \Cref{fig:global-throughput-random} is caused by the caching mechanism mentioned earlier.
If a new agreed fragment needs to be transmitted to validate every transaction then it puts a toll on the network infrastructure.
The low transaction rate in~\Cref{fig:global-throughput-random} is caused by the fact that the network infrastructure cannot keep up with our demand.

>>>>

The structure of the implementation is primarily made up of three modules---\texttt{acs}, \texttt{trustchain} and \texttt{node}.
\texttt{acs}, as its name suggests, implements ACS.
ACS uses erasure code in one of its sub-protocols (reliable broadcast).
Thus we use the liberasurecode\footnote{\url{https://github.com/openstack/liberasurecode}} library for its Reed-Solomon error correcting code functionality.
An implementation detail is that liberasurecode cannot create more than 32 code blocks, which is hardcoded in the source file\footnote{\url{https://github.com/openstack/liberasurecode/blob/0794b31c623e4cede76d66be730719d24debcca9/include/erasurecode/erasurecode.h\#L35}
}, we discuss the effect of this in~\Cref{sec:experimental-setup}.
The \texttt{acs} module provides a small interface to the caller to start and stop the consensus process and also retrieve results.
The \texttt{trustchain} module implements the Extended TrustChain data structure.
It also provides the essential algorithm necessary to interact with Extended TrustChain such as 
$\textsf{new\_tx}(\cdot)$, $\textsf{new\_cp}(\cdot)$ and $\textsf{agreed\_fragment}(\cdot)$.
Finally, the \texttt{node} module ties everything together.
It implements the consensus protocol, the transaction protocol and the validation protocol.

@@

The difference in magnitude between \Cref{fig:global-throughput-fixed} and \Cref{fig:global-throughput-random} is caused by the caching mechanism mentioned earlier.
If a new agreed fragment needs to be transmitted to validate every transaction then it puts a toll on the network infrastructure.
The low transaction rate in~\Cref{fig:global-throughput-random} is caused by the fact that the network infrastructure cannot keep up with our demand.
In practice, we do not expect such behaviour to occur as it is possible to cache agreed fragments.
